Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations

### 2021-01-06 README.Rmd
fixed another typo
finished going through a practice submission with the new paper

- [bullet-rf.rds](data/bullet-rf.rds) contains the saved version of the random forest trained using the bullet matching training data.
- [bullet-test.csv.zip](data/bullet-test.csv.zip) and [bullet-train.csv.zip](data/bullet-train.csv.zip) contain the data used for the bullet examples in the manuscript. See ["Additional Information on Bullet Data"](#additional-information-on-bullet-data) below for more information about the data.
- [example-signatures.csv.zip](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [raw](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
  - [CCFs_withlands.csv.zip](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [h224-set1-features.rds.zip](data/raw/h224-set1-features.rds.zip) and [h224-set11-features.rds.zip](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [signatures.rds.zip](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [README.txt](data/README.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
- [sine-data-test.rds](data/sine-data-test.rds) and [sine-data-train.rds](data/sine-data-train.rds) contain saved version of the sine data testing and training sets generated by the code in the manuscript.
- [sine-lime-explain.rds](data/sine-lime-explain.rds) contains the LIME explanations for the random forest predictions from the sine data test set.

@@

[**submission**](submission/)

>>>>

- [bullet-test.csv.zip](data/bullet-test.csv.zip) and [bullet-train.csv.zip](data/bullet-train.csv.zip) contain the data used for the bullet examples in the manuscript. See ["Additional Information on Bullet Data"](#additional-information-on-bullet-data) below for more information about the data.
- [example-signatures.csv.zip](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [raw](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
  - [CCFs_withlands.csv.zip](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [h224-set1-features.rds.zip](data/raw/h224-set1-features.rds.zip) and [h224-set11-features.rds.zip](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [signatures.rds.zip](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [README.txt](data/README.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.

@@

[**submissions**](submissions/)

### 2021-01-06 paper.Rnw
finished going through a practice submission with the new paper

\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.

>>>>

\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are \kge{also included in the online Supporting Information section and} \sout{available} in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
